Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-02-07 Journal1/paper2TNSM/pr.tex
Add scheduling to tnsm

Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ \textcolor{teal}{is the sum of the power of interfering signals and quantization noise represented as follow}

@@

>>>>

Also, $BN_0$ denotes the power of Gaussian additive noise.
\textcolor{Sepia}{UEs in different O-RUs can be assigned to different PRBs. As a result, a UE in O-RU $r$ using PRB $k$ may experience interference from other O-RUs in the set of $r' \in R -r$.
Network Slicing methods significantly reduce inter-service interference but do not eliminate it at all.
There are some techniques to minimize inter-slice interference. One of these techniques is to have two-time scale scheduling. The PRB scheduling to the slices is performed on the first time scale, and in the second time scale, the PRB scheduling to the UEs of slices is carried out. Since there are limited resources, inter-service interference cannot be eliminated entirely. The other method is to allocate part of the RB of eMBB services to URLLC and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}.}
We have two types of interference, the first one is between slices (inter-slice) and the second one is between UEs in each slices or services (intra-slice) that is shown in figure \ref{fig:intf}.
    \includegraphics[scale = 0.40]{Interference.png}
  \caption{Type of Interference Signal}
  \label{fig:intf}
\textcolor{teal}{ $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as follow}

@@

\subsubsection{PRB Scheduling}
\textcolor{Sepia}{  In this section, we study the problem of PRB scheduling to illuminate the inter-slice interference and guarantee the isolation of slices \cite{marabissi2019highly}.
We need to have an algorithm to illuminate the inter-slice interference before solving the problem \ref{problem}. Firstly, we should assign PRBs to slices, and in the second step, the assignment of PRBs of each slice to each UEs of a specific slice is performed. So, the assignment of PRB can be completed in two steps to remove inter-slice interference and isolate the slices. Firstly we assign PRBs to slices. Secondly, we allocate power of UEs, assign PRBs of slices to UEs, find the optimal number of VNFs for each slice and assign O-RU to UEs, which uses the proposed algorithm \ref{proAlg}.
Firstly, we need to find the average PRB number used by UEs in each service. Since mMTC and URLLC transmit a short packet, each UE in mMTC and URLLC requires 1 PRB. So if slice s serves mMTC or URLLC services, with $U_s$ UEs, it requires $K_s = U_s \times 1$ PRBs. For eMBB, assume the average rate of each UE in slice s serving eMBB UEs is $\bar{R}_s = Blog_2(1 + \bar{\rho_s})$, where, $\bar{\rho_s}$ is the average SNR of UEs in slice s. Also, $\mathcal{R}_{{s}}^{min}$ is the minimum data rate of each UE in slice s (eMBB slice).
So, the average number of PRB that slice s with $U_s$ UEs requires is $K_s = U_s \times \frac{\bar{R}_s}{\mathcal{R}_{{s}}^{min}}$. $K_s$ is the average number of PRBs needed for slice s, and K is the total number of PRBs in the system. Our goal is to obtain the number of PRBs assigned to each slice s ($\bar{K_s}$).
The problem can be written as follow
\begin{subequations}\label{prob:prb}
\max\limits_{\boldsymbol{\bar{K_s}}} \quad &  \sum_{s=1}^{S}\delta_s \bar{\mathcal{R}}_{{s}}^{min}\log(\frac{\bar{K_s}}{K_s}) \ \\
\text{subject to} \quad  & \sum_s{\bar{K_s}} \leq K
 \label{prb0} \\
& \bar{K_s}  \leq K_s  \quad \forall s, ,\label{prb1} 
